---
title: "Tutorial"
description: >
  This vignette gives some tutorial on Xsurv.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  fig.width = 6,
  fig.height = 5
)

```

## Survival data

### Cox model
In biomedical studies, the cox proportional hazard model (Cox 1972) is the most commonly used model for the regression analysis of survival outcomes.
 $$ \lambda (t \mid x) = \lambda_{0}(t) \exp{H(x)} $$
where H(.) is a risk score function that relates covariates and regression coefficients. In the standard Cox model, the risk score is a linear term, i.e., $ H(x)=x^{T}\beta$ . In particular, Xsurv_sim_data can generate data with linear model.

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(Xsurv)
set.seed(981)
beta=c(0.1,0.5,0.2,1,0.01) #set beta value

sim_dat<-Xsurv_sim_data(size=100,dim=5,lambda=2,vu=1, 
                        beta=beta, c_rate=0.25) 
```
### Automatically tunning the parameter with Xsurv.cv function

```{r echo=TRUE,results='hide'}

 X<-sim_dat[,1:5]
 y<-sim_dat[,6:7]

xs_cv<-Xsurv.cv(X,y,option = 'lgb',search = 'rd',top_n = 1) #random search tunning parameter with lightgbm model


```

```{r}
# both xgboost and lightgbm can be automatically tunning with Xsurv.cv
# xs_cv<-Xsurv.cv(X,y,option = 'xgb',search = 'grid') 
xmod<-xs_cv$model
cindx<--xs_cv$cindex
xs_cv$SHAP
#The only selected feature is V4 (if you remember the simulation setting beta=c(0.1,0.5,0.2,1,0.01), V4 is the only one not close to 0.)
```
### Simple case study
```{r}
library(survival)
data(lung) #Using lung data as an example

mydata<-(lung[,-1])
mydata[,2]<-mydata[,2]-1
length(mydata[,1])
names(mydata)<-colnames(mydata)

datay_train<-mydata[1:180,c(1,2)] 
datax_train<-mydata[1:180,-c(1,2)]


datay_test<-mydata[181:228,c(1,2)]
datax_test<-mydata[181:228,-c(1,2)]

#A survival tree plot will be generated. cp here is the pre-specified complexity of tree.
xs<-Xsurv.cv(datax_train,datay_train,top_n=5,cp=0.01)

xm<-xs$model

xtree<-xs$tree$tree1
#ctree
xctree<-xs$tree$tree2
plot(xctree)


shap=xs$SHAP

shap

#prediction

# Xsurv can also  predict the survival curve of a patient.

pre_x<-Xsurv_predict_sv(xm,datax_train,datay_train,datax_test[10,])

plot(pre_x)

#Actual survival time
datay_test[10,]

```{r}
