---
title: "Tutorial"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Survival data

### Cox model
In biomedical studies, the cox proportional hazard model (Cox 1972) is the most commonly used model for the regres-sion analysis of survival outcomes.
 $$ \lambda (t \mid x) = \lambda_{0}(t) \exp{H(x)} $$
where H(.) is a risk score function that relates covariates and regression coefficients. In the standard Cox model, the risk score is a linear term, i.e., $ H(x)=x^{T}\beta$ . In particular, Xsurv_sim_data can generate data with linear model.

```{r}
library(Xsurv)
set.seed(981)
beta=c(0.1,0.5,0.2,1,0.01) #set beta value

sim_dat<-Xsurv_sim_data(size=100,dim=5,lambda=2,vu=1, 
                        beta=beta, c_rate=0.25) 
```
### Automatically tunning the parameter with Xsurv.cv function

```{r}

 X<-sim_dat[,1:5]
 y<-sim_dat[,6:7]

xs_cv<-Xsurv.cv(X,y,option = 'lgb',search = 'rd') #random search tunning parameter with lightgbm model
# Not run:both xgboost and lightgbm can be automatically tunning with Xsurv.cv
# xs_cv<-Xsurv.cv(X,y,option = 'xgb',search = 'grid') 
xmod<-xs_cv$model
cindx<--xs_cv$cindex

```

